---
title: NYT Covid cases
author: Your name
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)

# Parameters
  # To get these URLs, I:
    # Step 1: Go here: https://github.com/nytimes/covid-19-data
    # Step 2: Click on the CSV file 
    # Step 3: Click "Raw" or "View raw"
    # Step 4: Copy the URL

  # URL for the county data
url_counties <- 
  "https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv"
  # URl for the state data
url_states <- 
  "https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"
file_population <- "data/populations.csv"
#===============================================================================

# For reading in the data--we'll get to this in a bit!

# col_types = 
#   cols(
#     date = col_date(format = ""),
#     county = col_character(),
#     state = col_character(),
#     fips = col_integer(),
#     cases = col_double(),
#     deaths = col_double()
#   )
counties <-
  url_counties %>% 
  read_csv(
    col_types =
      cols(
        date = col_date(format = ""),
        county = col_character(),
        state = col_character(),
        fips = col_integer(),
        cases = col_double(),
        deaths = col_double()
      )
  )

# col_types = 
#   cols(
#     date = col_date(format = ""),
#     state = col_character(),
#     fips = col_integer(),
#     cases = col_double(),
#     deaths = col_double()
#   )
states <-
  url_states %>% 
  read_csv(
    col_types = 
      cols(
        date = col_date(format = ""),
        state = col_character(),
        fips = col_integer(),
        cases = col_double(),
        deaths = col_double()
      )
  )

# col_types =
#   cols(
#     region = col_character(),
#     fips = col_integer(),
#     population = col_double()
#   )
population <-
  file_population %>% 
  read_csv(
    col_types =
      cols(
        region = col_character(),
        fips = col_integer(),
        population = col_double()
      )
  )
```

## States

### Glimpse and summary

```{r}

```

```{r}

```

### Check the states

```{r}
n_distinct(states$state)
```

```{r}
unique(states$state)
```

```{r}
states %>% 
  filter(!state %in% state.name) %>% 
  count(state, sort = TRUE)
```

### Missing values

```{r}
states %>% 
  summarize_all(~sum(is.na(.)))
```

`cases` and `deaths` are the _cumulative_ counts, so they should never go down (see the [documentation](https://github.com/nytimes/covid-19-data)). Is that true? 

```{r}
states %>% 
  group_by(
    # TODO: ADD NAME OF VARIABLE
  ) %>% 
  filter(lead(cases, order_by = date) < cases)
```

```{r}
states %>% 
  group_by(
    # TODO: ADD NAME OF VARIABLE
  ) %>% 
  filter(lead(deaths, order_by = date) < deaths)
```

## Counties


### Glimpse and summary

```{r}
glimpse(counties)
```

```{r}
summary(counties)
```

### Check counties and states

```{r}
n_distinct(counties$county)
```

```{r}
n_distinct(counties$state)
```

```{r}
unique(counties$state)
```

### Missing values

```{r}
counties %>% 
  summarize_all(~sum(is.na(.)))
```

```{r}
# TODO: investigate further
```


## Visualizations

### U.S. cases over time

```{r}
us <-
  states %>% 
  group_by(date) %>% 
  summarize(cases = sum(cases))

# us %>% 
#   ggplot(aes(TODO: Add x and y variables)) +
#   geom_line()
```

```{r}
us_daily <-
  us %>% 
  mutate(new_cases = cases - lag(cases, order_by = date)) 

us_daily %>% 
  drop_na(new_cases) %>% 
  filter(new_cases > 0) %>% # TODO: filter to just March through May
  ggplot(aes(date, new_cases)) +
  geom_col() 
```

### Which state has the most cases?

```{r fig.asp=0.7}
states_cumulative <-
  states %>% 
  group_by(fips, state) %>% 
  summarize(cases = sum(cases, na.rm = TRUE)) %>% 
  ungroup()

# This plot is not very useful! Remove to comment to make it better
states_cumulative %>% 
  # mutate(state = fct_reorder(state, cases)) %>% 
  ggplot(aes(cases, state)) +
  geom_point()
```

### Which state has the most cases per capita?

```{r fig.asp=0.7}
states_cumulative %>% 
  left_join(population, by = "fips") # %>% 
  # filter(!is.na(population)) %>% 
  # mutate(
  #   cases_per_capita = population / cases,
  #   state = fct_reorder(state, cases_per_capita)
  # ) %>% 
  # ggplot(aes(cases_per_capita, state)) +
  # geom_point()
```

### State daily cases

```{r}
states %>% 
  group_by(state) %>% 
  mutate(new_cases = cases - lag(cases, order_by = date)) %>% 
  ungroup() # %>% 
  # drop_na(new_cases) %>% 
  # filter(state == "TODO: CHOOSE A STATE") %>% 
  # ggplot(aes(date, new_cases)) +
  # geom_col()
```


## Counties

```{r}
counties_cumulative <-
  counties %>% 
  drop_na(fips) %>% 
  group_by(county, state, fips) %>% 
  summarize(cases = sum(cases, na.rm = TRUE)) %>% 
  ungroup()

counties_cumulative %>% 
  top_n(n = 15, wt = cases) %>% 
  mutate(
    county = str_c(county, ", ", state) %>% fct_reorder(cases)
  ) 
# TODO: plot cases for top N counties
```

## Compare trends across states

```{r}
# TODO: Add or change the states
# TODO: Try a log scale
states %>% 
  filter(state %in% c("California", "Georgia")) %>% 
  ggplot(aes(date, cases, color = state)) +
  geom_line() 
```


